%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{setspace}


\name{Jing Zhang} % Your name
\address{2034 West Henrietta Rd \\ Rochester, New York State 14623} % Your address
\address{(585~$\cdot$~478~$\cdot$~9272) \\ zjsw1206@gmail.com} % Your phone number and email


\begin{document}
	
\begin{rSection}{Online Profile}
	\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
		Github & https://github.com/zjswhhh \\
		LinkedIn & https://www.linkedin.com/in/jing-zhang-058917152/
	\end{tabular}
\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Education}
{\bf University of Rochester} \hfill {\em December 2018 (Expected)} \\ 
M.S. COMPUTER SCIENCE \\
Selected Coursework: Machine Learning, Artifitial Intelligence, Design and Analysis Efficient Algorithms, Advanced Algorithm, Database System, Web Programming

{\bf University of Electronic Science and Technology of China} \hfill {\em June 2017} \\ 
B.ENG. COMMUNICATION ENGINEERING \\
Memeber of Yingcai Honors School (top 2\% students selected from UESTC) \\
Cumulative GPA: 3.62/4
\end{rSection}

%	TECHNICAL STRENGTHS SECTION

\begin{rSection}{Technical Strengths}
	
	\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
		Computer Languages & C/C++, Java, Python, MATLAB, VHDL, \LaTeX \\
		Web Development & HTML, CSS, JavaScript, JQuery, AJAX, PHP, MySQL, XML/JSON	\\ 
		Software \& Tools & Hadoop, Spark, MATLAB, SPSS, Mathcad, Lingo, Excel\\ 
		Language &Mandarin, English
	\end{tabular}
	
\end{rSection}

%	EXPERIENCE

\begin{rSection}{Experience}
	\begin{rSubsection}{Teaching Assistant}{March 2018 - Present}{University of Rochester}{Rochester, NY, USA}
		\item Worked as the Teaching Assistant in CIS442F Big Data.
		\item Served as instrutor on big data concepts, environments, processes and tools,  including Hadoop and Apache Spark.
	\end{rSubsection}
	 
	\begin{rSubsection}{Data Engineer Intern}{February 2017 - April 2017}{Hangzhou Hikvision Digital Technology Co., Ltd.}{Hangzhou, China}
		\item Worked in the RCNN group at the Research Center of Hikvision.
		\item Utilized C++ to preprocess training datasets.
	\end{rSubsection}
	
	%------------------------------------------------
	
	\begin{rSubsection}{Research Assistant}{March 2016 - June 2017}{Data Mining Lab of UESTC, supervised by Prof.Junming Shao}{Chengdu, China}
		\item Conducted a research on identifying the ranking of nodes in heterogeneous networks.
		\item Implemented experiments on DBLP dataset to prove efficiency of our algorithm, using JAVA. 
		\item Thesis: Identifying Important Nodes in Heterogeneous Networks Based on Clustering Methods.
		
	\end{rSubsection}
	
	\begin{rSubsection}{Interdisciplinary Contest in Modeling (ICM), Meritorious Winner}{February 2016}{Consortium for Mathematics and Its Applications (COMAP)}{Chengdu,China}
		\item Served as the team leader, mainly in charge of modeling, algorithm design, MATLAB programming and academic writing.
		\item Collaborated in a team of 3 to model and solve a real world math problem in three days.  
		\item Thesis: Evolution of Multilayer Social Information Networks.
		
	\end{rSubsection}
	
	
\end{rSection}

\begin{rSection}{Selected Projects}
	
	%------------------------------------------------
	\begin{rSubsection}{Super Tic-Tac-Toe}{February 2017}{University of Rochester}{Rochester, NY}
		\item Designed, implemented an AI program that plays Super Tic-Tac-Toe against human or computer opponents, based on heuristic minimax algorithm \& alpha-beta pruning, using Python.
	\end{rSubsection}
	
	\begin{rSubsection}{Video Game Reviews Website}{September - November 2017}{University of Rochester}{Rochester, NY}
		\item Built up a community on which user can write reviews about video games and grade them.
		\item Implemented scores \& comment update functionalities based on AJAX and a game taste recommendation system.
		\item Accomplished a database management system, using PHP and MySQL.
		\item Designed front-end pages based on HTML, CSS, JavaScript.
	\end{rSubsection}
	
	\begin{rSubsection}{Information Management System for Preschools}{September - November 2017}{University of Rochester}{Rochester, NY}
		\item Designed \& developed a Database System to record health conditions, meal nutrition records \& school schedules for preschool childs, based on MySQL.
		\item Developed multiple web interfaces (UI) for users with different authorities to manage the Database System, using HTML, CSS, JavaScript and PHP. 
	\end{rSubsection}
	
	\begin{rSubsection}{Smart Home System Application on Android Platform}{July 2015}{Yingcai Honors School of UESTC}{Chengdu, China}
		\item Collaborated in a team of 3 to develop a smart home system based on Zigbee, which is able to accomplish following
		functions: temperature and humidity monitoring; illegal intrusion alarm; an intelligent lighting control system.
		\item Developed an terminal controlling application on Android Platform, using JAVA.
	\end{rSubsection}
	
\end{rSection}





%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
